### 2022-06-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betacov_mapping@c3b033a4e022255700ed689fe367e4000ac0daba 🚀

\hypertarget{coevolution-informed-spillover-risk-is-different-in-space}{%
\subsection{Coevolution-informed spillover risk is different in
space}\label{coevolution-informed-spillover-risk-is-different-in-space}}

>>>>

\hypertarget{coevolution-informed-emergence-risk-is-different-in-space}{%
\subsection{Coevolution-informed emergence risk is different in
space}\label{coevolution-informed-emergence-risk-is-different-in-space}}
